### 2016-10-24 writing/thesis/acknowledgements.tex
Rename writing/latex to writing/thesis

I would like to thank Stefanía Andersen Aradóttir for making sure I didn't look
like a fool in my attempt at Icelandic for my title.

>>>>

I would like to thank Stefanía Andersen Aradóttir for company and sanity checks
during long working weekends and for making sure I didn't look like a fool in my
attempt at an Icelandic title.

### 2016-10-24 writing/thesis/coincidence.tex
Rename writing/latex to writing/thesis

This rule can be understood very in graphical form. In the
pattern in \FigureRef{fig:rule1} we can gain shading in three boxes since if
there is a point in any of these boxes we would get an occurrence of the
dominating pattern \(\perm{3,2,1}\).

@@

Note that there are two natural extensions of this rule. We can replace \(\pi\)
with a set of classical patterns, or we can consider \(\pi\) to be a mesh pattern.

\section{Equivalence classes of Av(\{231, (21, \textit{R})\}).}
By application of \PropositionRef{prop:dom1} we obtain \(43\) coincidence
classes. Experimentation shows that there are in fact at least \(39\) coincidence
classes, for example the following two patterns are coincident in
\(\av{\perm{2,3,1}}\) but this is not explained by \PropositionRef{prop:dom1}.
\begin{equation*}
    m_1 = \pattern{}{2,1}{0/0,0/2,1/0,2/1} \text{ and } m_2 = \pattern{}{2,1}{0/0,0/2,1/0,1/1,2/1}
\end{equation*}

>>>>

This rule can be understood very in graphical form. In the
pattern in \FigureRef{fig:rule1} we can gain shading in two boxes since if
there is a point in any of these boxes we would get an occurrence of the
dominating pattern \(\perm{3,2,1}\).

@@

There are two natural extensions of this rule. We can replace \(\pi\)
with a set of classical patterns, or we can consider \(\pi\) to be a mesh pattern.

\section{Equivalence classes of Av(\{231, (21, \textit{R})\}).}
By application of \PropositionRef{prop:dom1} we obtain \(43\) coincidence
classes. Experimentation shows that there are in fact at least \(39\) coincidence
classes, for example the following two patterns are coincident in
\(\av{\perm{2,3,1}}\) but this is not explained by \PropositionRef{prop:dom1}.
\begin{equation*}
    m_1 = \pattern{}{2,1}{0/0,0/1,0/2,1/0,2/1} \text{ and } m_2 = \pattern{}{2,1}{0/0,0/1,0/2,1/0,1/1,2/1}
\end{equation*}

### 2016-10-24 writing/thesis/confut.tex
Rename writing/latex to writing/thesis

It is interesting to consider the application of the Third Dominating rule,
as well as the simple extension of allowing a sequence of \texttt{add\_point}
operations, to meshpatterns without any dominating pattern in order to try to
capture some of the coincidences described in
\textcite{DBLP:journals/combinatorics/HilmarssonJSVU15}
 and \textcite{DBLP:journals/corr/ClaessonTU14}.
 \begin{example}
   We can establish the coincidence between the patterns
   \begin{equation*}
     m_1 = \pattern{}{1,2}{0/1,0/2,1/1,1/2,2/0}, \text{ and } m_2 = \pattern{}{1,2}{0/2,1/0,1/1,2/0,2/1}
   \end{equation*}
   That is not explained by the methods presented by \textcite{DBLP:journals/corr/ClaessonTU14}.

>>>>

It is interesting to consider the application of the Third Dominating rule,
as well as the simple extension of allowing a sequence of \texttt{add\_point}
operations, to mesh patterns without any dominating pattern in order to try to
capture some of the coincidences described in
\textcite{DBLP:journals/combinatorics/HilmarssonJSVU15}
 and \textcite{DBLP:journals/corr/ClaessonTU14}.
 \begin{example}
   We can establish the coincidence between the patterns
   \begin{equation*}
     m_1 = \pattern{}{1,2}{0/1,0/2,1/1,1/2,2/0}, \text{ and } m_2 = \pattern{}{1,2}{0/2,1/0,1/1,2/0,2/1}
   \end{equation*}
   That is not explained by the methods presented by \textcite{DBLP:journals/corr/ClaessonTU14}.

### 2016-10-24 writing/thesis/wilf.tex
Rename writing/latex to writing/thesis

Throughout this section we will consider Wilf-equivalences of patterns
whilst avoiding the \emph{dominating pattern} \(\perm{2,3,1}\). We will
use \(\mathcal{C}\) to denote \(\av{\perm{2,3,1}}\) and \(C(x)\) will
be the usual Catalan generating function satisfying \(C(x) = 1 + C(x)^2\).
This is easy to see by structural decomposition around the maximum, as
shown in \FigureRef{fig:decompmax}.

@@

\begin{note}
    \label{not:setequiv}
    The avoiders of the pattern \(q = \mperm{2,3,1}{\{(1,0),(1,1),(1,2),(1,3)\}}\),
    \textpattern{}{2,3,1}{1/0,1/1,1/2,1/3},
    in \(\mathfrak{S}_n\) are in one-to-one correspondence with partitions of
    \(\nrange{n}\). (\textcite[Prop.~2]{DBLP:journals/ejc/Claesson01})
\end{note}
\begin{proof}
    Let \(\pi\) be a permutation in \(\av[n]{q}\)
    in one-line notation and insert a dash between each ascent in \(\pi\). This
    corresponds to set partitions where the blocks are the elements between the
    dashes, the blocks are listed in increasing order of their least element,
    with the elements written in each block in descending order.
\end{proof}

>>>>

Throughout this section we will consider Wilf-equivalences of patterns
whilst avoiding the \emph{dominating pattern} \(\perm{2,3,1}\). We will
use \(\mathcal{C}\) to denote \(\av{\perm{2,3,1}}\) and \(C(x)\) will
be the usual Catalan generating function satisfying \(C(x) = 1 + xC(x)^2\).
This is easy to see by structural decomposition around the maximum, as
shown in \FigureRef{fig:decompmax}.

@@

\begin{note}
    \label{not:setequiv}
    The avoiders of the pattern \(q = \mperm{2,3,1}{\{(1,0),(1,1),(1,2),(1,3)\}}\),
    \textpattern{}{2,3,1}{1/0,1/1,1/2,1/3},
    in \(\mathfrak{S}_n\) are in one-to-one correspondence with partitions of
    \(\nrange{n}\). (\textcite[Prop.~2]{DBLP:journals/ejc/Claesson01})
\end{note}

The idea of the bijection is as follows.
    Let \(\pi\) be a permutation in \(\av[n]{q}\)
    in one-line notation and insert a dash between each ascent in \(\pi\). This
    corresponds to set partitions where the blocks are the elements between the
    dashes, the blocks are listed in increasing order of their least element,
    with the elements written in each block in descending order.
